Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-27 EconGrowth.Rnw
Trying to make the GDP comparison graph.

<<creategraph>>=

createCountryInputGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
                  type="l",
                  scales=list(cex=1.5, tck=-1),
                  ylab="Indexed (1980=1)",
                  auto.key=list(columns=1))
  return(graph)
}

createCountryInputGraph("US")

>>>>

<<graphs>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  colors <- c("black", "black", "black", "black") #line and point colors
  lineWidths <- c(1, 1, 1, 1) #line widths
  lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX ~ iYear, data=dataTable,
                  key=list(text=list(c("k", "l", "q", "x")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

createGDPComparisonGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  colors <- c("black", "black", "black", "black") #line and point colors
  lineWidths <- c(1, 1, 1, 1) #line widths
  lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  pointSpec <- list(col=colors)
  graph <- xyplot(iGDP ~ iYear, data=dataTable,
                  key=list(text=list(c("GDP")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
#                                      superpose.symbol = pointSpec),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)

}

createGDPComparisonGraph("US")

createCountryFactorsGraph("US")
#lapply(countries, createCountryFactorsGraph)
